Category-Pivot Transfer Learning from Knowledge Base to Microblog Stream for Accurate Event Detection

### 2016-10-05 paper/lncsFormat.tex
finish sec 2.1.1.1; 5151 words (related works)(event detection).(without extra information).(clustering articles)

\section{Related Works}
\label{sec:relatedWorks}
\textbf{Event Detection.} 
There are two kinds of event detection methods based on how it utilize the history data, unsupervised and supervised learning.

The unsupervised methods, including UMass\cite{Allan:2000wu} and BurstyBTM\cite{Yan:2015wm}, use \textit{the data within the recent time windows} to help to decide whether the incoming article is related to a new event. 
This kind methods can be implemented by clustering of articles\cite{Allan:2000wu,Petrovic:2010uj,Wurzer:2015wq}, word frequencies\cite{Mathioudakis:2010fc}\cite{Weng:2011wz}, or topic modelling\cite{Diao:2012wj}\cite{Yan:2015wm} in the recent time windows. 
Taking the clustering of articles as an example, they model the occurred events as clusters, and link the incoming article with an already existed event cluster or assign it as the new detected event.
The decision is based on whether the dissimilarity between the incoming article and existed event clusters is over the user-specified threshold.

The reason why this kind methods cannot achieve high precision and high recall simultaneously lies in that they lack the accumulation of history knowledge. 
This kind methods ``understand" the document only by the recent data and the frequencies of the data, but the ``understanding" is not so confident that they still need the specific threshold to help to make decision. In the journalist metaphor of news value theory, they have the limited knowledge of normal states (aka "routine things") due to the limited history information used. 
On the one hand, UMass\cite{Allan:2000wu} prefers the lower threshold to enlarge the recall but suffers the precision. 
On the other hand, BurstyBTM needs the appropriate number of topics to run the topic modelling, and detects the ``large" events that associate with many articles but ignores the ``small" ones.

The supervised thoroughly relies on the \textit{history data}. 
The typical implementation is to train the event triggers\cite{Li2013JointEE}\cite{Nguyen2015EventDA} from history labeled data, then apply the trained model to detect the event related articles, which contain the triggers such as the word \textit{attacked} for the \textit{public security} events. 
This kind methods suffer from the loss of recall. 
There are two reasons. 
%没有对历史数据进行很好的组织
(1) The model does not utilize the history data sufficiently. 
Usually, the event trigger based method mainly focus on the event related verbs, but often ignores the other word types.
(2) The model lacks the update mechanism. 
It only restores the history knowledge but without updating. 
Some new event related articles may be mistakenly filtered out because not containing previous trained triggers. 
For example, the tweet ``Russia's intervention in Syria began in September 2015" without an event trigger, which is really related to a \textit{public security} event, may be omitted by the system.

@@

\textbf{Retrieving event related microblogs}. 
To better understand the event, we retrieve the event microblogs \(\mathcal{D}_{c,t,i}\) by using the event phrase \(\mathcal{C}_{c,t,i}\).
Generally, according to the number of bursting words in the event phrase \(\mathcal{C}_{c,t,i}\), there are two situations to be addressed. 
(1) \(|\mathcal{C}_{c,t,i}|=1\), we directly add the microblog in time window \(t\), which contains the bursting category-word \(w^{(c)}\), into the set \(\mathcal{D}_{c,t,i}\).
(2) \(|\mathcal{C}_{c,t,i}|\geq 2\), not all the bursting words are included in the event related microblog.
For example, the tweet ``\textit{Soldier wanted to attack Fort Hood troops}" contains the bursting words \textit{attack} and \textit{hood}, not all the event phrase ``\textit{ft, hood, attack}". 
To tackle this problem, we consider the microblog, that contains any pair of category-words in the event phrase, as the event related microblog.

@@

\textbf{Text Stream Dataset.} We conduct the empirical analysis on a text stream benchmark \textit{Edinburgh twitter corpus} which is constructed by \cite{petrovic2012using} and widely used by previous event detection researches \cite{petrovic2013can} \cite{Wurzer:2015wq}. 
Due to the developer policy of Twitter, \cite{petrovic2012using} only redistributes tweets' IDs\footnote{\url{http://demeter.inf.ed.ac.uk/cross/docs/fsd_corpus.tar.gz}}.
%\footnote{\url{https://dev.twitter.com/overview/terms/policy}}
We collected the tweets' contents according to the IDs with the help of Twitter API. 
Though we cannot get the whole dataset due to the limit of Twitter API, after necessary pre-processing, our rebuilt dataset still contains 36,627,434 tweets, which spans identically from 2011/06/30 to 2011/09/15.
More details of the original dataset are described in \cite{petrovic2010edinburgh}.

@@

\textbf{Evaluation Metrics.} 
The first benchmark on \textit{Edinburgh twitter corpus} contains 27 manually labeled events\cite{petrovic2013can}\footnote{\url{http://demeter.inf.ed.ac.uk/cross/docs/Newswire_Events.tar.gz}}, which all exist in our rebuilt dataset on the \textit{Edinburgh twitter}'s IDs.
These labeled events focus on the events that are both mentioned in twitter and newswire,e.g. \textit{``Oslo Attacks"} and \textit{``US Increasing Debt Ceiling"}, but still miss many important events such as \textit{``Hurricane Irene"}, \textit{``Al-Qaida's No. 2 Leader Being Killed"}, and popular events such as \textit{``Harry Potter and the Deathly Hallows (Part 2)"}.
To enlarge the ground truth of realistic events, we manually evaluate the candidate events detected by LTDetector, Twevent, EDCoW, BurstyBTM, and TimeUserLDA, and  use the labeled events as the second benchmark.
We use precision and recall to evaluate each method on both benchmarks.
\begin{table}[h]
\scriptsize
\centering
\scalebox{0.95}{
    \begin{tabular}{|l|l|l|l|l|}
    \hline
    Method & \begin{tabular}[c]{@{}l@{}}Recall@ \\ Benchmark1\end{tabular} & \begin{tabular}[c]{@{}l@{}}Precision@ \\ Benchmark2\end{tabular} & \begin{tabular}[c]{@{}l@{}}Recall@ \\ Benchmark2\end{tabular} & \begin{tabular}[c]{@{}l@{}}DERate\\(Duplicate \\ Event Rate)\end{tabular} \\ \hline
    UMass System & 0.882 & 0.138 & 0.941 & 0.071 \\ \hline
    LSH & 0.824 & 0.095 & 0.803 & 0.302 \\ \hline
    TimeUserLDA & 0.353 & 0.536 & 0.071 & 0.054 \\ \hline
    Twevent & 0.824 & 0.697 & 0.641 & 0.113 \\ \hline
    EDCoW & 0.412 & 0.756 & 0.119 & 0.290 \\ \hline
    BurstyBTM & 0.647 & 0.809 & 0.170 & 0.045 \\ \hline
    \textsc{LTDetector} & 1.000 & 0.894 & 0.950 & 0.042 \\ \hline
    \end{tabular}
}
\caption{Overall Performance on Event Detection}
\end{table}

>>>>

\section{Related Works}
\label{sec:relatedWorks}
\textbf{Event Detection.} According to how much data are used, the approaches are divided into two groups: the detection only without extra information, and the detection by leveraging extra information.

Most existing methods belong to the first group.
They utilize the bursty pattern in the text stream to detect events, and are implemented by  clustering articles\cite{Allan:2000wu,Petrovic:2010uj,Wurzer:2015wq}, analyzing word frequencies\cite{Mathioudakis:2010fc,Weng:2011wz}, or finding bursty topics\cite{Diao:2012wj,Yan:2015wm}. 
(1) By clustering articles, UMass\cite{Allan:2000wu}, LSH\cite{Petrovic:2010uj}, k-Term-FSD\cite{Wurzer:2015wq} and other similar methods model the occurred events as clusters of articles, and link the incoming article with an already existed event cluster or label it as the first story of a new event.
The decision is based on whether the dissimilarity between the incoming article and existed event clusters is over the user-specified threshold. 
Taking LSH as an example, as \cite{Petrovic:2010uj} discussed, the threshold controls the result: the big one leads to very few and broad clusters, while the small one results in very small and specific clusters.
Even after carefully set the appropriate threshold, the clusters generated by this kind method are still mixed of events and non-events due to large portion of non-event microblogs, which requires some post-processing methods as the supplement. 
(2) By analyzing word frequencies, 
(3) By finding bursty topics, TimeUserLDA, BurstyBTM needs the appropriate number of topics to run the topic modelling, and detects the ``large" events that associate with many articles but ignores the ``small" ones.

%The unsupervised methods, including UMass\cite{Allan:2000wu} and BurstyBTM\cite{Yan:2015wm}, use \textit{the data within the recent time windows} to help to decide whether the incoming article is related to a new event.

The reason why this kind methods cannot achieve high precision and high recall simultaneously lies in that they lack the accumulation of history knowledge. 
This kind methods ``understand" the document only by the recent data and the frequencies of the data, but the ``understanding" is not so confident that they still need the specific threshold to help to make decision. In the journalist metaphor of news value theory, they have the limited knowledge of normal states (aka "routine things") due to the limited history information used. 
On the one hand, UMass\cite{Allan:2000wu} prefers the lower threshold to enlarge the recall but suffers the precision.

@@

\textbf{Retrieving event related microblogs}. 
To better understand the event, we retrieve the event microblogs \(\mathcal{D}_{c,t,i}\) by using the event phrase \(\mathcal{C}_{c,t,i}\).
Generally, according to the number of bursting words in the event phrase \(\mathcal{C}_{c,t,i}\), there are two situations to be addressed. 
(1) \(|\mathcal{C}_{c,t,i}|=1\), we directly add the microblog in time window \(t\), which contains the bursting category-word \(w^{(c)}\), into the set \(\mathcal{D}_{c,t,i}\).
(2) \(|\mathcal{C}_{c,t,i}|\geq 2\), it's not necessary that all the bursting words are included in the event related microblog.
For example, the tweet ``\textit{Soldier wanted to attack Fort Hood troops}" contains the bursting words \textit{attack} and \textit{hood}, not all the event phrase ``\textit{ft, hood, attack}". 
To tackle this problem, we consider the microblog, that contains any pair of category-words in the event phrase, as the event related microblog.

@@

\textbf{Microblog Stream Dataset.} We conduct the empirical analysis on a text stream benchmark \textit{Edinburgh twitter corpus} which is constructed by \cite{petrovic2012using} and widely used by previous event detection researches \cite{petrovic2013can} \cite{Wurzer:2015wq}. 
Due to the developer policy of Twitter, \cite{petrovic2012using} only redistributes tweets' IDs\footnote{\url{http://demeter.inf.ed.ac.uk/cross/docs/fsd_corpus.tar.gz}}.
%\footnote{\url{https://dev.twitter.com/overview/terms/policy}}
We collected the tweets' contents according to the IDs with the help of Twitter API. 
Though we cannot get the whole dataset due to the limit of Twitter API, after necessary pre-processing, our rebuilt dataset still contains 36,627,434 tweets, which spans identically from 2011/06/30 to 2011/09/15.
More details of the original dataset are described in \cite{petrovic2010edinburgh}.

@@

\textbf{Evaluation Metrics.} 
The first benchmark on \textit{Edinburgh twitter corpus} contains 27 manually labeled events\cite{petrovic2013can}\footnote{\url{http://demeter.inf.ed.ac.uk/cross/docs/Newswire_Events.tar.gz}}, which all exist in our rebuilt dataset on the \textit{Edinburgh twitter}'s IDs.
These labeled events focus on the events that are both mentioned in twitter and newswire,e.g. \textit{``Oslo Attacks"} and \textit{``US Increasing Debt Ceiling"}, but still miss many important events such as \textit{``Hurricane Irene"}, \textit{``Al-Qaida's No. 2 Leader Being Killed"}, and popular events such as \textit{``Harry Potter and the Deathly Hallows (Part 2)"}.
To enlarge the ground truth of realistic events, we manually evaluate the candidate events detected by LTDetector, Twevent, EDCoW, BurstyBTM, and TimeUserLDA, and  use the labeled events as the second benchmark.
We use precision and recall to evaluate each method on both benchmarks.

%TODO LSH-FSD\cite{Petrovic:2010uj}没有评测FSD的情况，我们也可以提一句，我们不评测FSD，我们只评测检测出的事件是否是真实的事件。
\begin{table}[h]
\scriptsize
\centering
\scalebox{0.95}{
    \begin{tabular}{|l|l|l|l|l|}
    \hline
    Method & \begin{tabular}[c]{@{}l@{}}Recall@ \\ Benchmark1\end{tabular} & \begin{tabular}[c]{@{}l@{}}Precision@ \\ Benchmark2\end{tabular} & \begin{tabular}[c]{@{}l@{}}Recall@ \\ Benchmark2\end{tabular} & \begin{tabular}[c]{@{}l@{}}DERate\\(Duplicate \\ Event Rate)\end{tabular} \\ \hline
    UMass System & 0.882 & 0.138 & 0.941 & 0.071 \\ \hline
    LSH & 0.824 & 0.095 & 0.803 & 0.302 \\ \hline
    TimeUserLDA & 0.353 & 0.536 & 0.071 & 0.054 \\ \hline
    Twevent & 0.824 & 0.697 & 0.641 & 0.113 \\ \hline
    EDCoW & 0.412 & 0.756 & 0.119 & 0.290 \\ \hline
    BurstyBTM & 0.647 & 0.809 & 0.170 & 0.045 \\ \hline
    \textsc{LTDetector} & 1.000 & 0.894 & 0.950 & 0.042 \\ \hline
    \end{tabular}
}
\caption{Overall Performance on Event Detection}
\end{table}
